---
title: "Fin516 Project"
author: "Dushyant Singh Khinchi"
date: "2/21/2020"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.

(a) The 1 SD of a 44 day price move is $535.6


(b) 1 SD price range is from $1524.4 to $2595.6

```{r}


setwd("D:/FIN 516/Project")


## Black-Scholes model parameters
## s0  - current stock price
## k   - strike price
## sig - pricing volatility
## t   - time, in years
## q   - dividend yield if any, default is no dividend yield
## typ - typ of option: 'c' for call and 'p' for put

source('OptionAnalytics.r')
s0 <- 2060
k <- seq(1980,2140,by=20)
sig <- 0.26
r <- 0.016
t44 <- 44/365
c1 <- round(BS(s0,k,sig,r,t44),2)
p1 <- round(BS(s0,k,sig,r,t44,typ='p'),2) 
## create a data.frame of strikes with call and put prices
opt1 <- data.frame(strike=k,calls=c1,puts=p1)

#option chain
opt1 
```


```{r}

Call <- function(s,k){
  return(ifelse(s-k>0,s-k,0))}

Put <- function(s,k){
  return(ifelse(k-s>0,k-s,0))}

t16 <- 16/365
t30 <- 30/365
```




# 2. Straddle

```{r}

#Straddle

#Cost
cost0 <- -c1[k==2060]-p1[k==2060]
cost0
```



(a) Option premium: -$148.21


It's a credit
```{r}

s <- seq(1900,2220,by=10)

Straddle_val <- function(s,k,sig,r,t){ 
  return( -BS(s,k,sig,r,t,typ='c') - BS(s,k,sig,r,t,typ='p'))
  }

Straddle_delta <- function(s,k,sig,r,t){ 
  return(-BSdelta(s,k,sig,r,t,typ='c') -BSdelta(s,k,sig,r,t,typ='p')) } 

### 30 DTE
pl30 <- round(Straddle_val(s,2060,sig,r,t30) - cost0*exp((t44-t30)*r),2)

delta30 <- round(Straddle_delta(s,2060,sig,r,t30),4)


### 16 DTE
pl16 <- round(Straddle_val(s,2060,sig,r,t16) - cost0*exp((t44-t16)*r),2)

delta16 <- round(Straddle_delta(s,2060,sig,r,t16),4)


### 0 DTE
pl0 <- round(-Call(s,2060)-Put(s,2060) - cost0*exp(t44*r), 3)


sig1 <- .16
pl30_16 <- round(Straddle_val(s,2060,sig1,r,t30) - cost0*exp((t44-t30)*r),2)

sig2 <- .36
pl30_36 <- round(Straddle_val(s,2060,sig2,r,t30) - cost0*exp((t44-t30)*r),2) 

t10<-10/365
pl10 <- round(Straddle_val(s,2060,sig,r,t10) - cost0*exp((t44-t10)*r),2)

```

```{r}
data.frame(s,pl30,pl16,pl0,delta30,delta16,pl30_16,pl30_36,pl10)

```

(e) With 10 DTE for the stock price range from $1900 to $2060 profit increases with the increase in stock price and attains a maximum of $77.71 and for the stock price range from $2060 to $2220 profit increases with the decrease in stock price.


(f)Assuming zero commissions, Max Profit = Net Premium Received

Max Profit per option contract = 100*148.21 = $14821 


(g)It is preferable to place the trade in a low volatility environment because as it can be seen that lower value of sigma gives higher profits
for DTE30




# 3. Ironfly

```{r}

#Ironfly

#Cost
cost_IF<-p1[k==2020]-c1[k==2060]-p1[k==2060]+c1[k==2100]
cost_IF

```



(a) Option premiumt: -$36.51


It's a Credit


```{r}

s <- seq(1940,2180,by=10)
Ironfly_val <- function(s,k,k1,k2,sig,r,t){ 
  return(BS(s,k1,sig,r,t,typ='p') -BS(s,k,sig,r,t,typ='c') - BS(s,k,sig,r,t,typ='p') + BS(s,k2,sig,r,t,typ='c'))
}


Ironfly_delta <- function(s,k,k1,k2,sig,r,t){ 
  return(BSdelta(s,k1,sig,r,t,typ='p')-BSdelta(s,k,sig,r,t,typ='c') -BSdelta(s,k,sig,r,t,typ='p')+BSdelta(s,k2,sig,r,t,typ='c')) } 


### 30 DTE
pl30 <- round(Ironfly_val(s,2060,2020,2100,sig,r,t30) - cost_IF*exp((t44-t30)*r),2)

delta30 <- round(Ironfly_delta(s,2060,2020,2100,sig,r,t30),4)


### 16 DTE
pl16 <- round(Ironfly_val(s,2060,2020,2100,sig,r,t16) - cost_IF*exp((t44-t16)*r),2)

delta16 <- round(Ironfly_delta(s,2060,2020,2100,sig,r,t16),4)



### 0 DTE
pl0 <- round(Put(s,2020)-Call(s,2060)-Put(s,2060)+Call(s,2100) - cost_IF*exp(t44*r),2)



pl30_16 <- round(Ironfly_val(s,2060,2020,2100,0.16,r,t30) - cost_IF*exp((t44-t30)*r),2)



pl30_36 <- round(Ironfly_val(s,2060,2020,2100,0.36,r,t30) - cost_IF*exp((t44-t30)*r),2)


```

```{r}


data.frame(s,pl30,pl16,pl0,delta30,delta16,pl30_16,pl30_36)


```

(e) Assuming zero commissions, Max profit per option contract = 100*36.51 = $3651

 Max loss per option contract = (2060-2020-36.51)*100 = $349
 
 
 
(f)It is preferable to place the trade in a low volatility environment



# 4. Strangle

```{r}
#Strangle

cost_st<- p1[k==2020]+c1[k==2100]
cost_st

```


(a) Option premium: 111.7

It's a debit

```{r}


s <- seq(1900,2220,by=10)
Strangle_val <- function(s,k1,k2,sig,r,t){ 
  return(BS(s,k1,sig,r,t,typ='p') + BS(s,k2,sig,r,t,typ='c'))
}


Strangle_delta <- function(s,k1,k2,sig,r,t){ 
  return(BSdelta(s,k1,sig,r,t,typ='p')+BSdelta(s,k2,sig,r,t,typ='c')) } 




### 30 DTE
pl30 <- round(Strangle_val(s,2020,2100,sig,r,t30) - cost_st*exp((t44-t30)*r),2)
delta30 <- round(Strangle_delta(s,2020,2100,sig,r,t30),4)



### 16 DTE
pl16 <- round(Strangle_val(s,2020,2100,sig,r,t16) - cost_st*exp((t44-t16)*r),2)
delta16 <- round(Strangle_delta(s,2020,2100,sig,r,t16),4)


### 0 DTE
pl0 <- round(Put(s,2020)+Call(s,2100) - cost_st*exp(t44*r),2)

pl30_16 <- round(Strangle_val(s,2020,2100,0.16,r,t30) - cost_st*exp((t44-t30)*r),2)

pl30_36 <- round(Strangle_val(s,2020,2100,0.36,r,t30) - cost_st*exp((t44-t30)*r),2)

```


```{r}

data.frame(s,pl30,pl16,pl0,delta30,delta16,pl30_16,pl30_36)
```

(e)Max profit = Unlimited

Assuming zero commissions, Max loss per option contract = 100*111.7 = $11170 

(f) It is preferable to place the trade in a High volatility environment because as it can be seen that higher value of sigma gives higher profits
for DTE30.



# 5. Ironcondor

```{r}

#Ironcondor

#Cost
cost_IC<- -p1[k==1980]+p1[k==2020]+c1[k==2100]-c1[k==2140]
cost_IC

```

(a) Option premium: $29.83 

It's a Debit
```{r}

s <- seq(1900,2220,by=10)
Ironcondor_val <- function(s,k1,k2,k3,k4,sig,r,t){ 
  return(-BS(s,k1,sig,r,t,typ='p') +BS(s,k2,sig,r,t,typ='c') + BS(s,k3,sig,r,t,typ='p') - BS(s,k4,sig,r,t,typ='c'))
}


Ironcondor_delta <- function(s,k1,k2,k3,k4,sig,r,t){ 
  return(-BSdelta(s,k1,sig,r,t,typ='p')+BSdelta(s,k2,sig,r,t,typ='c') +BSdelta(s,k3,sig,r,t,typ='p')-BSdelta(s,k4,sig,r,t,typ='c')) } 


### 30 DTE
pl30 <- round(Ironcondor_val(s,1980,2020,2100,2140,sig,r,t30) - cost_IC*exp((t44-t30)*r),2)



### 16 DTE
pl16 <- round(Ironcondor_val(s,1980,2020,2100,2140,sig,r,t16) - cost_IC*exp((t44-t16)*r),2)

### 0 DTE
pl0 <- round(-Put(s,1980)+Call(s,2020)+Put(s,2100)-Call(s,2140) - cost_IC*exp(t44*r),3)


delta30 <- round(Ironcondor_delta(s,1980,2020,2100,2140,sig,r,t30),4)

delta16 <- round(Ironcondor_delta(s,1980,2020,2100,2140,sig,r,t16),4)

pl30_16 <- round(Ironcondor_val(s,1980,2020,2100,2140,0.16,r,t30) - cost_IC*exp((t44-t30)*r),2)

pl30_36 <- round(Ironcondor_val(s,1980,2020,2100,2140,0.36,r,t30) - cost_IC*exp((t44-t30)*r),2)


```

```{r}

data.frame(s,pl30,pl16,pl0,delta30,delta16,pl30_16,pl30_36)

```

(e) Max profit per option contract = (2020-1980-29.83)*100 = $1017

Assuming zero commissions, Max loss per option contract = 100*29.83 = $2983


(f) It is preferable to place the trade in a High volatility environment
